---
title: "Pinnochio"
author: "Matt Crump"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = F,
                      warning = F)
```


# Load the data

```{r}
load("E1/data-E1-typing.Rda")
```

# some design notes

1. Each subject wrote 4 paragraphs, 1 per condition
2. Everyone listed top 2 favorite movies, and bottom 2 hated movies
3. For top 2 favorite, randomly assigned to positve and negative reccomendation conditions
4. For bottom 2, randomly assigned to positve and negative reccomendation conditions

positive recomendation: write a short paragraph reccommending this movie to someone
negative recomendation: write a short paragraph not reccommending this movie to someone

IKSI: interkeystroke interval (milliseconds)

# Big question

What features predict whether people are lying or not (congruent vs. incongruent)

# Pre-processing

```{r}

max(typing$IKSI)
hist(typing$IKSI)
```


## Mean IKSI

Write a blurb explaining what this feature is...

```{r}
library(dplyr)

subject_meansA <- typing %>% 
                 group_by(workerId,condition) %>%
                 summarize(mean_iksi = mean(IKSI))

condition_means <- subject_meansA %>%
                   group_by(condition) %>%
                   summarize(mean_iksi = mean(mean_iksi))

t.test(mean_iksi~condition, paired=TRUE, data=subject_meansA)

difference_scores <- subject_meansA[subject_meansA$condition=="incongruent",]$mean_iksi - subject_meansA[subject_meansA$condition=="congruent",]$mean_iksi

mean(difference_scores)
sd(difference_scores)

cohens_d <- mean(difference_scores)/sd(difference_scores)
cohens_d

congruency_labels <- subject_meansA$condition
congruency_labels <- as.factor(congruency_labels)
congruency_labels <- as.numeric(congruency_labels)

category_guess<-c()
for (i in difference_scores){
  if(i<=0){
    category_guess <- c(category_guess, 2,1)
  } else {
    category_guess <- c(category_guess, 1,2)
  }
}

category_guess <-as.factor(category_guess)

subject_meansA <- cbind(subject_meansA, 
                        clabels = congruency_labels,
                        c_guess = category_guess)

subject_meansA <- subject_meansA %>%
                    mutate(accuracy = (clabels==c_guess))

mean(subject_meansA$accuracy)
  




knitr::kable(condition_means)

```


## first-letter IKSI

Write a blurb explaining what this feature is...

```{r}


subject_means <- typing %>% 
                 filter(word_unedited_letterPos == 1) %>%
                 group_by(workerId,condition) %>%
                 summarize(mean_iksi = mean(IKSI))

View(subject_means)

# check
# unique(table(subject_means$workerId))

t.test(mean_iksi~condition, paired=TRUE, data=subject_means)

condition_means <- subject_means %>%
                   group_by(condition) %>%
                   summarize(mean_iksi = mean(mean_iksi))

knitr::kable(condition_means)

```


# list some features

- number of words in paragraph
- number of typos...(number of backspaces)
- first letter IKSI
- non-first letter IKSIs
- total time to write paragraph
- average word length

unique_names <- unique(df_sorted$topic)


#Number of words in paragraph
```{r}
library (ngram)


library(splitstackshape)
library(dplyr)


library(sqldf)

x <- sqldf('SELECT workerId, condition, uneditedText FROM response GROUP BY workerId, condition, uneditedText ')

x$wordCount <- 0

View (x)

for(i in 1:nrow(x)) 
{
  x[i,4] <- wordcount(x[i,3])
}

#by(x, 1:nrow(x), function(row){ row$wordCount <- wordcount(x[i,3]})

totalWords_means <- x %>% 
                 group_by(workerId,condition) %>%
                 summarize(mean_words = mean(wordCount))

t.test(mean_words~condition, paired=TRUE, data=totalWords_means)

condition_means_totalWords <- totalWords_means %>%
                   group_by(condition) %>%
                   summarize(mean_words = mean(mean_words))
```
#Typos
```{r}
num_typos <- typing %>% 
                 group_by(workerId, condition) %>%
                 summarize(total_typos = sum(backspace))

t.test(total_typos~condition, paired=TRUE, data=num_typos)

condition_typos_means <- num_typos %>%
                   group_by(condition) %>%
                   summarize(total_typos = mean(total_typos))
```



## non-first-letter IKSI


```{r}


subject_means_nonFirst <- typing %>% 
                 filter(word_unedited_letterPos != 1) %>%
                 group_by(workerId,condition) %>%
                 summarize(mean_iksi = mean(IKSI))

View (subject_means_nonFirst)

# check
# unique(table(subject_means$workerId))

t.test(mean_iksi~condition, paired=TRUE, data=subject_means_nonFirst)

condition_means <- subject_means_nonFirst %>%
                   group_by(condition) %>%
                   summarize(mean_iksi = mean(mean_iksi))


```



##RT
```{r}
duration_df <- sqldf('SELECT workerId, condition, RT FROM response GROUP BY workerId, condition, RT ')
View (duration_df)

totalRT_means <- duration_df %>% 
                 group_by(workerId,condition) %>%
                 summarize(mean_RT = mean(RT))

t.test(mean_RT~condition, paired=TRUE, data=totalRT_means)

condition_means_totalRT <- totalRT_means %>%
                   group_by(condition) %>%
                   summarize(mean_RT = mean(mean_RT))

```


##Word Length
```{r}
word_length_df <- sqldf('SELECT workerId, condition, word_unedited_length FROM typing GROUP BY workerId, condition, word_unedited_length ')

word_length_df <- sqldf('SELECT * FROM typing ')

View (word_length_df)

word_length <- word_length_df %>% 
                 group_by(workerId,condition) %>%
                 summarize(word_length_mean = mean(word_unedited_length))


```



# some checks 
```{r}


length(unique(subject_meansA$workerId))
length(unique(subject_means$workerId))

which(subject_meansA$workerId %in% subject_means$workerId ==FALSE)

subject_meansA[311,]



```















